New lower bounds for Schur and weak Schur numbers

### 2021-04-07 article/schur.tex
definition template

\begin{definition}
	Let \( n \in \mathbb{N}^*\), there exists a greatest integer that we note \(SE_+(n)\) (resp. \(SE_-(n)\)) such that \( [\![1, SE_+(n)]\!]\) 
	(resp. \( [\![1, SE_-(n)]\!]\)) can be partitionned (resp. can not be partionned) into \(n\) sum-free subsets \(A_1, A_2, ..., A_n\) which verify :
	\[
	\forall k \in [\![1, n-1]\!], \forall (x,y) \in A_k^2, x+y > SE_+(n)
	\Longrightarrow x+y-SE_+(n) \notin A_k
	\]
\end{definition}
We notice that in general, unlike regular Schur numbers, we don't have \(SE_+(n) + 1 \neq SE_-(n)\)

@@

The first inequality comes from the original Schur's paper \hyperlink{label1}{\textbf{[1]}}. The second and third ones were found by Rowley (reference nécessaire), 
and the other ones are new. \\

>>>>

\begin{definition}
	We call SF-template of \(k\) colors and lenght \(n\) a partition of \( [\![1,n]\!]\) into \(k\) sum-free subsets \(A_1, A_2, ..., A_k\) which verify :
	\[
	\forall i \in [\![1, k-1]\!], \forall (x,y) \in A_i^2, x+y > n
	\Longrightarrow x+y-n \notin A_i
	\]
	We note \(SE_+(k)\) the maximal lenght for a SF-template of \(k\) colors. 
\end{definition}

@@

The first inequality comes from the original Schur's paper \hyperlink{label1}{\textbf{[1]}}. The second and third ones were found by Rowley (reference nécessaire), 
while the other ones are new. \\
